Reconstruction of Charge Number of Heavy Cosmic Rays using Cherenkov Light

### 2016-04-22 report/draft1.tex
Backup 22/4/16

@@

\subsection{Atmospheric Absorption}
Cosmic Rays get absorbed and stuff.

>>>>

\section{Camera Image Simulation}
The first requirement for reconstruction using the LPD method is to identify the DC pixel in a shower image, and consequently determine the number of DC photons present. A full simulation of air showers was performed using the CORSIKA package, and the simtelarray package was used to simulate HESS camera images generated from the shower. The hesioxxx package was used to extract camera image pixel positions and signals.

\subsection{CORSIKA}
A full simulation of air showers was performed using the CORSIKA package \cite{Heck98}, assuming a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia. The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{2.7}$. Four random seed numbers were passed to the program, generated using the overall job number and the run number corresponding to the parallel computing task index. Thus, for each set of simulations, 4 unique random number seeds were used. An altitude of 1800m was assumed, again corresponding to the HESS site. The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$.

In order to identify the DC pixel, each simulation run with an energy cut of 10 PeV on all muons and electrons. The consequence of this was to ensure that only the Cherenkov Light from the primary particle, as well as its fragments, was simulated. A second identical simulation was run with the same random seeds but without the energy cut on muons and electrons, giving a complete air shower including the DC light.

\subsection{Sim\textunderscore telarray}
Using the sim\textunderscore telarray package, the expected hardware response to the air shower can be simulated. Again, the response of the HESS telescope was selected for simulation, accounting for

@@

\subsection{Atmospheric Absorption}
The Cherenkov Light, mostly emitted in the visible blue part of the EM spectrum, experiences relatively little atmospheric absorption. The major of Rayleigh scattering-based atmospheric absorption occurs in the lower part of the troposphere, and thus the atmospheric absorption is almost independent of emission up to first interaction height.
